### 2025-12-14 src/articles/article10.qmd
Scholarship updates (#12)

1. Once per semester, brothers and Candidates will fill out grade release forms.
   a. Grade release forms must be filled out prior to the due date for midterm grades.

>>>>

1. Once per semester, brothers and Candidates will fill out grade release forms.
   a. Grade release forms must be filled out prior to the due date for midterm grades.
   a. Grades must be directly self reported to the Scholarship Chair within one week of the GLO report release if the grades are missing from the report.
   a. If the GLO report is not released within two weeks into classes, grades must be self reported to the Scholarship Chair within one week.
   a. Midterm grades must be reported directly to the Scholarship Chair within 2 weeks of the grades being released.
